Optical Music Recognition for LilyPond File Generation

### 2024-05-10 papers/cs444/paper-cs444.tex
more work

\title[omr-lilypond-midi]{Optical Music Recognition for LilyPond File Generation}
\author{Evan Matthews}
% \email{evanmm3@illinois.edu}
% %\orcid{1234-5678-9012}
% \affiliation{%
% 	\institution{University of Illinois Urbana-Champaign}
% 	\country{}
% }

% \begin{abstract}
% \todo{Abstract}
% \end{abstract}

@@

\section{Introduction}
\subsection{Initial Proposal}
\todo{Introduction citations}
\cite{andrea2021note}

@@

\begin{itemize}
	\item [\textbf{RQ1}] What forms of recognition can be expected from a generalized CRNN implementation?
	\item [\textbf{RQ2}] How does Lilypond recognition compare against other standard and custom formats?
	\item [\textbf{RQ3}] What conflicts currently prevent state-of-the-art models from further generalization?
\end{itemize}

@@

\begin{figure}
	\centering
	\begin{subfigure}
		\centering
		\includegraphics[width = .8\linewidth]{./figures/c1.png}
	\end{subfigure}
	~
	\begin{subfigure}
		\centering
		\includegraphics[width = .8\linewidth]{./figures/c32.png}
	\end{subfigure}
	\caption{Levels of Quantization $[2^0, 2^5]$ in Rendering}
	\label{fig:quantization}
\end{figure}

@@

The following section details my analysis with respect to previously discussed research questions.

\subsection{Model Generalization (RQ1)}

\subsection{Format Comparison (RQ2)}

\subsection{Model Criticism (RQ3)}

\section{Conclusions}
\todo{conclusions}

>>>>

\title[omr-lilypond-midi]{Optical Music Recognition for LilyPond File Generation}
\author{Evan Matthews}

@@

\section{Introduction}
\subsection{Initial Proposal}

@@

\begin{itemize}
	\item [\textbf{RQ1}] What forms of recognition can be expected from a generalized CRNN implementation?
	\item [\textbf{RQ2}] How does Lilypond recognition compare against other standard and custom music formats?
	\item [\textbf{RQ3}] What conflicts currently prevent state-of-the-art models from further generalization?
\end{itemize}

@@

\begin{figure}
	\centering
	\begin{subfigure}
		\centering
		\includegraphics[width = .8\linewidth]{./figures/c1.png}
	\end{subfigure}
	~
	\begin{subfigure}
		\centering
		\includegraphics[width = .8\linewidth]{./figures/c32.png}
	\end{subfigure}
	\caption{Levels of Quantization $Q = [1, 32]$ in Rendering}
	\label{fig:quantization}
\end{figure}

@@

The following section details my analysis with respect to the previously mentioned research questions (\textbf{RQ1-3}).

\subsection{Model Generalization (RQ1)}
Given that resulting text output consisted of

\subsection{Format Comparison (RQ2)}
Lilypond is not, by all means, a perfect music formatting language. 
Being a format focused on the visual clarity of musical notation, I find that the aforementioned "document level" greatly hinders Lilypond from achieving basic recognition.
In particular, additional keywords for the representation and position of solely visual elements of a score, 
along with their necessary language features like brackets and spacers, strongly inhibit basic CRNN models from making noticeable music generalizations.

\subsection{Model Criticism (RQ3)}
My CRNN implementation, along with the CRNN model for which my research references, are not without barriers preventing consistent musical generalization.
In staying consistent with my description of the Lilypond language, my critiques against CRNNs are categorized by what should exist in order for music-level and document-level generalizations to occur.

\subsubsection{Music-level Generalization}

\subsubsection{Document-level Generalization}

\section{Conclusions}
\todo{conclusions}
Overall, despite low expectations for workable data, the following experiment and results proved to be quite beneficial in testing the Lilypond format.
